Bullet Groups as a test of $\Lambda$CDM

### 2014-03-04 paper/ms.tex
geometry and measurement setup

The configuration of the BGs in the simulations is shown in Figure
\ref{configuration}. There we depict a host and its most massive
sub-halo from in a particular case found at z$=0$. The arrows show the
position and the velocity vectors sub-halo in a frame of reference
where the main halo is at rest; thus  $\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and
$\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$.  The angle between these two
vectors characterized by,
\begin{equation}
  \mu\equiv \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|v{}\right\| \left\|r\right\|}
 \end{equation} 
%
encodes the geometry of the collision, i.e. cases of $|\mu|\approx 1$
can be considered as head-on collisions while $|\mu|\approx 0$
describe a grazing trajectory.

@@

Using these quantities one can describe three main stages in a
Bullet-like collision. First, the sub-halo crosses the virial radius
of the host halo in a head-on fashion, $|\vec{r}|/R_{\rm vir}\approx
1$ and $\mu\approx<0.0$. Second, as the sub-halo crosses for the first
time the center of the host halo $|\vec{r}|/R_{\rm vir} <
1.0$ and $\mu>0.0$. Third, as the sub-halo reaches apogee and
comes back to the center of the halo $|\vec{r}|/R_{\rm vir} < 1.0$ and
$\mu<0.0$.

the 
mass ranges and number of host halos and substructures 
are summary in the Table \ref{table1}. Of all the possible configurations that can be presented
in Figure \ref{configuration}, we are interested in estimate in the simulation the number 
of Bullet Groups that may be present in an Universe of 250 $h^{-1}$Mpc. For this we selected 
of the simulations all the substructures  
whose velocities indicate a movement out of the host halo. Each halo in this sample has a quantity
called $X_{off}$ that corresponds to the distance halo center (the minimum of the gravitational potential) to 
the center of mass normalized by the
virial radius ($R_{vir}$). Values of $X_{off}$
equal to zero indicate relaxed halos, while $X_{off}>0$ indicates the existence
of perturbed halos which can be considered candidates to be Bullet Groups and this ditribution is shown 
in a scatter plot in the Figure \ref{cos_theta1} and the distribution of $\nu_{circ,Halo}/\nu_{circ,Sub}$ 
is shown in  Figure \ref{cos_theta2}, both figures for differents z.

>>>>

The configuration of the BGs in the simulations is shown in Figure
\ref{configuration}. There we depict a host and its most massive
sub-halo from in a particular case found at z$=0$. The arrows show the
position and the velocity vectors sub-halo in a frame of reference
where the main halo is at rest; thus  $\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and
$\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$.  The angle between these two
vectors characterized by,
\begin{equation}
  \mu\equiv
  \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|\vec{v}{}\right\|
    \left\|\vec{r}\right\|} 
 \end{equation} 
%
encodes the geometry of the collision, i.e. cases of $|\mu|\approx 1$
can be considered as head-on collisions while $|\mu|\approx 0$
describe a grazing trajectory.

@@

As a first approximation there are two quantities that are available
from observations of these Bullet-like systems. The projected distance
between two dominand dark matter clumps and the ratio of the
galaxies' luminosities associated to them. From the simulation point
of view this can be translated into the 2D projected values of
$||\vec{r}||$, its value relative to the virial radius $\chi =
||\vec{r}||_{2D}/R_{\rm vir}$ and the ratio of the circular velocities of the two clumps $V_{\rm c,sub}/V_{\rm c,host}$. Then, in order to gain better insight we use
the sub-structure velocity as a fraction of the host's circular
velocity, $||\vec{r}||/V_{\rm c, host}$, as a mesure of the the strenght
of the interaction.  Finally, an even more detailed picture of the
collision can be obtained through the values of $\mu$.

All the physical quantities described above can be used to describe
the tree main stages in a bullet-like encounter. First, the sub-halo
crosses the virial radius of the host halo starting a head on
collission, $|\vec{r}|/R_{\rm vir}\approx 1$ and
$\mu\approx<0.0$. Second, as the sub-halo crosses for the first time
the center of the host halo $|\vec{r}|/R_{\rm vir} < 1.0$ and
$\mu>0.0$. Third, as the sub-halo reaches apogee and comes back to the
center of the halo $|\vec{r}|/R_{\rm vir} < 1.0$ and $\mu<0.0$. We use
this quantities in Section XXX to fully characterize the different
kind of interactions observed in the Bolshoi simulation.

The ranges of circular velocities for the host and sub-halos and the
corresponding number of halos at every redshift are listed in Table
\ref{table1}.

mass ranges and number of host halos and substructures 
are summary in the Table \ref{table1}. Of all the possible
configurations that can be presented in Figure \ref{configuration}, we
are interested in estimate in the simulation the number  of Bullet
Groups that may be present in an Universe of 250 $h^{-1}$Mpc. For this
we selected  of the simulations all the substructures   
whose velocities indicate a movement out of the host halo. Each halo
in this sample has a quantity called $X_{off}$ that corresponds to the
distance halo center (the minimum of the gravitational potential) to
the center of mass normalized by the virial radius ($R_{vir}$). Values
of $X_{off}$ equal to zero indicate relaxed halos, while $X_{off}>0$
indicates the existence of perturbed halos which can be considered
candidates to be Bullet Groups and this ditribution is shown  in a
scatter plot in the Figure \ref{cos_theta1} and the distribution of
$\nu_{circ,Halo}/\nu_{circ,Sub}$ is shown in  Figure \ref{cos_theta2},
both figures for differents z.
